### 2022-08-22 manuscript.Rmd
Fix command for TFR figures

```{r, fig2, fig.height=11, fig.cap="(ref:figure-2-caption)", include=TRUE}
# Create topographic plots for event-related power in each phase
tfr_plots <- plot_fig2(tfr_grand_ave, tfr_clusters, channel_locations, tmin = -0.4, tmax = 1.4, tstep = 0.2)

>>>>

```{r, fig2, fig.height=11, fig.cap="(ref:figure-2-caption)", include=TRUE}
# Create topographic plots for event-related power in each phase
tfr_plots <- plot_fig2(tfr_grand_ave, tfr_clusters, channel_locations)
